MaxEnt: What is it good for?

### 2015-08-10 ms.tex
A bit of tidying

Of course, $p(x)$ must be non-negative and sum to 1.
From this probability distribution, various probabilities can be derived
using the sum and product rules. For example, the probability of
($x=4$ {\bf or} $x=5$) is $p_4 + p_5$, and the probability of $x=5$ given
($x=5$ {\bf or} $x=8$) is $p_5/(p_5 + p_8)$. The rules of probability must
be obeyed if the rules for combining are to remain consistent
with the symmetries of logical {\bf and} and {\bf or}
\citep{2010arXiv1008.4831K}.

The relative entropy of distribution $p$ from distribution $q$ is:
\begin{eqnarray}
H(p; q) &=& -\sum_i p_i \log\left(\frac{p_i}{q_i}\right) 
\end{eqnarray}
Intuitively, $H$ measures how close the probability distribution $p$ is
to the distribution $q$. The maximum possible value of $H$ is zero, if
and only if $p$ happens to be the same as $q$.
However, it is not symmetric and does not satisfy
other properties of a distance.
and we are to choose the distribution $p$ to maximise $H$ subject to the
constraints of normalisation and any other constraints.

@@

\section{What is testable information?}
{\it Testable information} refers to information given in the form of
{\it a constraint that our probability distribution should satisfy}. This is
different from the kind of information we normally use in Bayesian inference,
which is the truth of a proposition. An example of testable information
might be $P(x > 7) = 0.4$. That is, our probability distribution should have
the property that there's a 40\% probability of $x$ being greater than 7.
If our current (prior) probability distribution $q$ already has this property,
then we needn't do anything. However, if $q$ does not satisfy this property,
we use MaxEnt to choose a new distribution, the posterior $p$.

The posterior $p$ will satisfy the constraint given in the testable information,
and will be as close to $q$ as possible while doing so.

>>>>

Of course, $p(x)$ must be non-negative and sum to 1 in order to be a valid
probability distribution.
From this probability distribution, various probabilities can be derived
using the sum and product rules. For example, the probability of
($x=4$ {\bf or} $x=5$) is $p_4 + p_5$, and the probability of $x=5$ given
($x=5$ {\bf or} $x=8$) is $p_5/(p_5 + p_8)$. The rules of probability must
be obeyed if the rules for combining are to remain consistent
with the symmetries of logical {\bf and} and {\bf or}
\citep{2010arXiv1008.4831K}.

The relative entropy of distribution $p$ from distribution $q$ is:
\begin{eqnarray}
H(p; q) &=& -\sum_i p_i \log\left(\frac{p_i}{q_i}\right) 
\end{eqnarray}
Intuitively, $H$ measures how close the probability distribution $p$ is
to the distribution $q$. The maximum possible value of $H$ is zero, if
and only if $p$ happens to be the same as $q$.
However, $H$ is not symmetric and does not satisfy
other properties of a distance.

@@

\section{What is testable information?}
{\it Testable information} refers to information given in the form of
{\it a constraint that our probability distribution should satisfy}. This is
the kind of information MaxEnt uses, and is
different from the kind of information we normally use in Bayesian inference,
which is the truth of a proposition. An example of testable information
might be $P(x > 7) = 0.4$. That is, our probability distribution should have
the property that there's a 40\% probability of $x$ being greater than 7.
If our current (prior) probability distribution $q$ already has this property,
then we needn't do anything. However, if $q$ does not satisfy this property,
we use MaxEnt to choose a new distribution, the posterior $p$.

The posterior $p$ must satisfy the constraint given in the testable information,
and should be as close to $q$ as possible while doing so. The criterion for
``closeness'' is the relative entropy $H(p; q)$:
we should choose the distribution $p$ to maximise $H$ subject to the
constraints of normalisation (i.e. $\sum_i q_i = 1$)
and the testable information.
